---
title: "case_study"
author: "Ling Yi"
date: "10/13/2020"
output: github_document
---

```{r include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r}
library(p8105.datasets)
data(nyc_airbnb)
```

##brainstroming some questions

what is the best aribnb in staten island for <100?
what price range is popular in each borough?
what apartment features are related to price
cheapest room type in each neighborhood
hosts have higher ratings?

```{r}
##not working for me
nyc_airbnb %>% 
  filter(neighbourhood_group == "Staten Island") %>% 
  filter (price<100) %>% 
  count(review_scores_location) %>% 
  arrange(desc(n))
```

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location/2)
```

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```


```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)
```


```{r}
nyc_airbnb %>% 
  filter(
    price<1000, 
    neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price))
  ggplot(aes(x = neighbourhood, y = price))+
  geom_boxplot()+
  coord_flip()
```

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, color = price))+
  geom_point()
```
```{r}

```

